Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/methodology.tex
Fix typo in formula
Editing paper details

\section{Methodology}
Write something about what we're comparing with, the codes we're
using, and how we set up the simulations.

@@

\subsection{Computational methodology}
Provide a general description of the LES codes that we use.

@@

\begin{align}
  \frac{\partial}{\partial t}\left(\bar{\rho} k \right) + \frac{\partial}{\partial x_j} \bar{\rho} k \widetilde{u_j} &= \frac{\partial}{\partial x_j} \left (2 \nu_t \frac{\partial k}{\partial x_j} \right) - 2 \nu_t \widetilde{S_{ij}} \widetilde{S_{ij}} + \frac{g}{\theta_\circ} \tau_{\theta_i} - C_{\epsilon} \frac{k^{3/2}}{l} \label{eqn:ksgs-les}
\end{align}
where
\begin{align*}
  C_\epsilon &= 0.93 & \nu_t &= C_\epsilon l \sqrt{k} \\
  \tau_{\theta i} &= - 2\ \frac{\nu_t}{\mathrm{Pr}_t}\ \frac{\partial \widetilde{\theta}}{\partial x_i} & \mathrm{Pr}_t &= \left( 1 + \frac{2l}{\Delta} \right)^{-1} \\
\end{align*}
The choice of the length scale ($l$) depends on whether the stratification is positive
or negative, based on the recommendation by Moeng~\cite{Moeng1984}, and is given
by
\begin{align*}
  l =
  \begin{cases}
    \Delta = \sqrt{\Delta_x \Delta_y \Delta_z}, & \frac{\partial \widetilde{\theta}}{\partial z} < 0 \\
    0.76\, \sqrt{k}\, \frac{g}{\theta_\circ}\, \left( \frac{\partial \widetilde{\theta}}{\partial z}\right)^{-1/2}, &  \frac{\partial \widetilde{\theta}}{\partial z} > 0 \\
  \end{cases}
\end{align*}

@@

\fxnote{Do we want a github link reference for amr-wind? exawind?}\\

@@

\subsection{Computational setup}
% \fxnote{Domains, grids, boundary conditions}

>>>>

\section{Methodology}
\fxnote{Write something about what we're comparing with, the codes we're
using, and how we set up the simulations.}

@@

\subsection{Computational methodology}
%Provide a general description of the LES codes that we use.

@@

\begin{align}
  \frac{\partial}{\partial t}\left(\bar{\rho} k \right) + \frac{\partial}{\partial x_j} \bar{\rho} k \widetilde{u_j} &= \frac{\partial}{\partial x_j} \left (2 \nu_t \frac{\partial k}{\partial x_j} \right) - 2 \nu_t \widetilde{S_{ij}} \widetilde{S_{ij}} + \frac{g}{\theta_\circ} \tau_{\theta_i} - C_{\epsilon} \frac{k^{3/2}}{l} \label{eqn:ksgs-les}
\end{align}
where
\begin{align*}
  C_\epsilon &= 0.93 & \nu_t &= C_\epsilon l \sqrt{k} \\
  \tau_{\theta i} &= - 2\ \frac{\nu_t}{\mathrm{Pr}_t}\ \frac{\partial \widetilde{\theta}}{\partial x_i} & \mathrm{Pr}_t &= \left( 1 + \frac{2l}{\Delta} \right)^{-1} \\
\end{align*}
The choice of the length scale ($l$) depends on whether the stratification is positive
or negative, based on the recommendation by Moeng~\cite{Moeng1984}, and is given
by
\begin{align*}
  l =
  \begin{cases}
    \Delta = \sqrt[3]{\Delta_x \Delta_y \Delta_z}, & \frac{\partial \widetilde{\theta}}{\partial z} < 0 \\
    0.76\, \sqrt{k}\, \frac{g}{\theta_\circ}\, \left( \frac{\partial \widetilde{\theta}}{\partial z}\right)^{-1/2}, &  \frac{\partial \widetilde{\theta}}{\partial z} > 0 \\
  \end{cases}
\end{align*}

@@

% \fxnote{Do we want a github link reference for amr-wind? exawind?}\\

@@

\subsection{\label{sec:CFDsetup}Computational setup}
% \fxnote{Domains, grids, boundary conditions}
